---
title: "Group Project"
author: "Chuong Tran"
date: "2023-04-05"
output: pdf_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache =TRUE)
```

```{r}
heart_data <- read.csv("/Users/chuongtran/Library/Containers/com.microsoft.Excel/Data/Desktop/College/SPRING2023/MATH-4322/Project/heart_data.csv")
heart_data$gender = as.factor(heart_data$gender)
heart_data$smoke = as.factor(heart_data$smoke)
heart_data$alco = as.factor(heart_data$alco)
heart_data$active = as.factor(heart_data$active)
```


```{r cars}
data.glm = glm(cardio ~ age+gender+height+weight+ap_hi+ap_lo+cholesterol+gluc+smoke+alco+active, family = "binomial", data = heart_data)
summary(data.glm)
```
- Gender is not an important variable for the model. 
- Age, height, weight, ap_hi, ap_lo, cholesterol, gluc, smole, alco, and active are significant variables for the model.
-$\hat{p}(X) = \frac{exp(-8.49 + 1.49e-04*age + 1.53e-02*gender - 5.73e-03*height + 1.54e-02*weight + 3.95e-02*ap_hi + 3e-04*ap_lo + 5.23e-01*cholesterol - 1.18e-01*gluc - 1.32e-01*smoke -1.69e-01*alco -2.1e-01*active)}{1 + exp(-8.49 + 1.49e-04*age + 1.53e-02*gender - 5.73e-03*height + 1.54e-02*weight + 3.95e-02*ap_hi + 3e-04*ap_lo + 5.23e-01*cholesterol - 1.18e-01*gluc - 1.32e-01*smoke -1.69e-01*alco -2.1e-01*active)}$. 



```{r}
set.seed(101)
sample <- sample.int(n = nrow(heart_data), size = round(.75*nrow(heart_data),0), replace=F)
train <- heart_data[sample,]
test <- heart_data[-sample,]
```

```{r}
data.train = glm(cardio ~ age+gender+height+weight+ap_hi+ap_lo+cholesterol+gluc+smoke+alco+active, family = "binomial", data = train)
summary(data.train)
```
```{r}
glm.pred = predict.glm(data.train, newdata = test, type = "response")
yHat <- glm.pred > 0.5
table(test$cardio, yHat)
```

- Error rate = $\frac{2096 + 2730}{6777 + 2096 + 2730 + 5897}$ = 27.6%. 

## Without Gender

```{r}
data.train2 = glm(cardio ~ age+height+weight+ap_hi+ap_lo+cholesterol+gluc+smoke+alco+active, family = "binomial", data = train)
data.train3 = glm(cardio ~ -id -index -gender, family = "binomial", data = train)
summary(data.train3)
summary(data.train2)
glm.pred2 = predict.glm(data.train2, newdata = test, type = "response")
yHat2 <- glm.pred2 > 0.5
table(test$cardio, yHat2)
```
- Error rate = $\frac{2096 + 2730}{6777 + 2096 + 2730 + 5897}$ = 27.6%. 

```{r}
# do for loop 10 times
set.seed(10)
error <- c()

for (i in 1:10) {
  
  sampleLoop <- sample.int(n = nrow(heart_data), size = round(.75*nrow(heart_data),0), replace=F)
  trainLoop <- heart_data[sampleLoop,]
  testLoop <- heart_data[-sampleLoop,]
  data.trainLoop = glm(cardio ~ age+height+weight+ap_hi+ap_lo+cholesterol+gluc+smoke+alco+active, family = "binomial", data = trainLoop)
  glm.predLoop = predict.glm(data.trainLoop, newdata = testLoop, type = "response")
  yHatLoop <- glm.predLoop > 0.5
  tab = table(testLoop$cardio, yHatLoop)
  
  error[i] = (tab[1,2] + tab[2,1]) / sum(tab)
} 

mean(error)

```
## Random Forest
```{r}
set.seed(10)
train.rf = sample(1:nrow(Boston),nrow(Boston)/2)
rf = randomForest(medv ~., data = heart_data,
subset = train,
mtry = (ncol(Boston)-1)/3,
importance = TRUE)
yhat.rf = predict(rf.boston,newdata = Boston[-train,])
mean((yhat.rf - boston.test)ˆ2)
```

